IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-11 review/response_2.tex

		\begin{response}
			Thank you for raising this point. The combining ratio $\delta$ determines the priority on multisine power waveform at the transmitter, while the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver. We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large. Heuristically, $\delta$ and $\rho$ should approximately equal at each point to boost R-E tradeoff. Indeed, the LC-BCD algorithm intends to draw the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{0} to \num{1}. However, based on the reasoning above, we set $\delta=\rho$ is the simulation and obtain the R-E region by one-dimensional search instead. The results show that even a one-dimensional search for the LC-BCD algorithm can achieve a very good performance. We have summarized the point in the manuscript as follows.
			\begin{framed}
				\textellipsis where the combining ratio $\delta$ determines the priority on multisine power waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver\footnotemark.

				\textellipsis Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.

				\textellipsis assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region).

@@

				\textellipsis  Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
			\end{framed}
			\footnotetext{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large. Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}
		\end{response}

		\begin{point}
			If possible, in Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz}, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
		\end{point}

		\begin{response}
			We would like to clarify that the performance loss under the conventional linear harvester model is revealed in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}. Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz} are intended to compare different IRS strategies when both waveform and passive beamforming are designed under nonlinear harvester model. The authors believe that to design passive beamforming under linear harvester model when the waveform is designed under nonlinear harvester model might confuse the readers. On the other hand, we agree with the reviewer that the performance loss under linear harvester deserves more attention, and have changed the label in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector} from `ASS' to `LEH' and revised the manuscript as follows to make this point clear.
			\begin{framed}
				Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design. To investigate the performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}. As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
			\end{framed}
		\end{response}

@@

		\begin{point}
			It was shown via simulation that PS is not always superior to TS, unlike the linear model. Is it possible to develop some analytical preconditions to determine which one is better?
		\end{point}

		\begin{response}
			We concluded that PS outperforms TS when the number of subcarrier is relatively small or when the SNR is relatively large. However, the analytical preconditions in the proposed system can be very hard to obtain because SNR can depend on many factors (e.g., distance of all paths, number of IRS elements, average noise power, etc.). Essentially, this behavior origins from the waveform selection and we would like to analyze it in a nutshell.

			TS only performs a naive time-sharing between the WIT point and the WPT point. At the WIT point, only modulated waveform is used to maximize the achievable rate. At the WPT point, the optimal waveform depends on the number of subcarriers $N$. Although the modulated waveform has an modulation gain of \num{2} that outstands for a small $N$, it creates no DC coupling between frequencies and is outperformed by multisine for a large $N$. Therefore, for a relatively small $N$, the modulated waveform is used at both WIT and WPT points, and one can heuristically infer that no multisine waveform is needed for any point (this is verified in simulation). In this case, the R-E region is convex, which aligns with the conventional linear harvester model (PS outperforms TS and dedicated power waveform is unnecessary). However, as $N$ becomes sufficiently large, multisine waveform further boosts the WPT point due to its power benefit under nonlinear harvester model. It creates some concavity in the high-power region and accounts for the superiority of TS.

@@

			Similar effect exists for SNR. At high SNR, the SWIPT user can achieve a decent rate even if a small fraction of transmit power is allocated to the modulated waveform. Therefore, one can approach high-rate region fast at a small cost of DC power at high SNR. This is however impossible at low SNR.

			The manuscript has been updated as follows.
			\begin{framed}
				Second, the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\ref{M-fi:re_subband}). When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region. It aligns with the conclusion based on the conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary. As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model. Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
			\end{framed}
		\end{response}

@@

		\begin{point}
			Is it possible to give the complexity order of the algorithms presented in this paper?
		\end{point}

		\begin{response}
			We have added complexity analysis in the revised manuscript. The reviewer is referred to Response~\ref{re:1.1} for details.
		\end{response}

		\begin{point}
			The expressions of signals in (1), (2), and (5) are not conventional. It may be better to give a per-band signal instead of their superposition. Besides, it is better to first introduce the functionalities of the modulated and multisine waveforms before giving (1).
		\end{point}

		\begin{response}
			We agree with the reviewer that the signal model requires more description. The manuscript has been updated as follows.
			\begin{framed}
				As suggested in \cite{M-Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency. The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
				\begin{equation}
					\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
				\end{equation}
				where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$. On the other hand, the power signal transmitted over subband $n$ at time $t$ is
				\begin{equation}
					\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
				\end{equation}
				where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
				\begin{equation}
					\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
				\end{equation}
			\end{framed}
		\end{response}

@@

		\begin{point}
			In Remark~\ref{M-re:subband_tradeoff}, the meaning of the sentence, ``there exists a tradeoff for auxiliary link control in the frequency domain'', is not clear to me.
		\end{point}

		\begin{response}
			By `auxiliary link control in the frequency domain', we intended to emphasize that the auxiliary link cannot be designed independently at different frequencies, and subchannel design flexibility arises in the presence of IRS. The composite channel can be tuned adaptively to satisfy the specific requirement of the multi-carrier transmission. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). We have added Fig.~\ref{fi:channel_amplitude} and updated the Remark~\ref{M-re:subband_tradeoff} to clarify this point.
			\begin{framed}
				The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies. Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). That is to say, IRS essentially enables a flexible subchannel design. In the MISO case, a similar effect also exists in the spatial domain. Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
			\end{framed}
			\label{re:2.10}
		\end{response}

@@

		\begin{point}
			Some editorial comments: 1) ``a (-->an) M-antenna''; 2) ``through a (-->an) L-element IRS''; 3) ``the CSIT of direct and cascaded channels are (-->is) known''; 4) ``It demonstrated (-->demonstrates) that''; 5) In Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, the text in the y-axis is too long. Please divide it into two rows. Besides, the text in the x-axis of the upper figure is covered by the lower one.
		\end{point}

		\begin{response}
			We sincerely appreciate your careful reading and rigorous feedbacks. The manuscript have been revised accordingly and we will avoid similar issues as possible.
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			Proposition~5 is questionable. The algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
		\end{point}

		\begin{response}
			Thank you for pointing out this issue. Indeed, the local optimality is not guaranteed as \eqref{M-co:original_rate} couples all blocks together. We have removed the claim on optimality and updated the manuscript as follows.
			\begin{framed}
				\textellipsis It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{M-co:original_rate} \cite{M-Grippo2000}.
			\end{framed}
			\label{re:3.1}
		\end{response}

@@

		\begin{response}
			We apologize for the inconvenience. The figures have been amplified and the legends have been calibrated.
		\end{response}

		\begin{point}
			It is said that the reference path loss is \SI{35}{\dB} at \SI{1}{\meter}, while for the center frequency at \SI{5.18}{\GHz}, even adopting the free space path loss model also will lead a much sever path loss at \SI{1}{\meter}. It is not clear how the authors calculate this.
			\label{pt:3.3}
		\end{point}

		\begin{response}
			We agree with the reviewer that the reference path loss used in the simulation is faulty and we sincerely apologize for this issue. The parameter \SI{35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without careful consideration. In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{40}{\dB} at \SI{1}{\meter}. The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and \num{3.5} onwards to penalize the channels with large distance.

			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference. Moreover, all plots are re-simulated over \num{100} channel realizations. Please refer to the following specification for details.
			\begin{framed}
				We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{M-Erceg2004}. Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance. All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d. CSCG variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{M-Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region). Each R-E point is averaged over \num{100} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
			\end{framed}
		\end{response}

@@

		\begin{point}
			The authors considered the practical reflection coefficient beamforming in the simulation results. It is not clear how the authors obtain the discrete phase shift results. Direct quantization method and some other customized optimization techniques for discrete phase shifts may have significant performance gap, see \cite{Wu2020c}. Also, this work adopts the same uniform quantization as the above work, which thus needs to be clarified in the paper.
		\end{point}

		\begin{response}
			Thank you for the clarification. The discrete phase shift is obtained by quantizing the continuous phase shift obtained by Algorithm~\ref{M-al:bcd} to the uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$. We are aware that quantization can lead to performance loss compared with direct optimization over the feasible phase shift set. In the revised manuscript, we have emphasized this point as follows.
			\begin{framed}
				On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{M-al:bcd} to reduce the circuit complexity and control overhead.\footnotemark
			\end{framed}
			\footnotetext{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.}
		\end{response}

@@

		\begin{point}
			There are also some other practical phase shift models and nonlinear energy harvesting models such as saturation model for IRS-aided SWIPT in existing works, which may be discussed as related works such as amplitude-dependent phase shift model.
		\end{point}

		\begin{response}
			We have added reference \cite{Xu2021} in the updated manuscript that models the saturation effect of energy harvesters and physical properties of the IRS. Its contributions have been summarized in the manuscript as follows.
			\begin{framed}
				Based on practical IRS and harvester models, \cite{M-Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage. The proposed framework provides a flexible tradeoff between performance and complexity.
			\end{framed}
			The future works has been updated as follows.
			\begin{framed}
				Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{M-Abeywickrama2020}, angle-dependent reflection \cite{M-Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{M-Shen2020a} could be considered in future works.
			\end{framed}
		\end{response}

@@

		\begin{point}
			Some early magazine papers and recent tutorial papers related to IRS-aided WPT/WIT may be further discussed.
		\end{point}

		\begin{response}
			Thank you for the suggestion. A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail. However, the aforementioned paper appeared on arXiv after ours and have cited our work, and we decided not to cite it. We have incorporated one magazine paper \cite{Wu2020} into the manuscript.
			\begin{framed}
				\textellipsis The hardware architecture, design challenges, and application opportunities of practical IRS are covered in \cite{Wu2020}.
			\end{framed}
		\end{response}
	\end{reviewer}
